---
title: "A/B Experiment: iRex 07 February Repeat"
subtitle: "Summary & Stats Analysis"
date: "26/02/2021"
output: html_document
toc: true
toc_float: true
ceruleancss: picture.css
---
<br>
<br>

# {.tabset .tabset-fade}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
invisible(gc())
library(tidyverse)
library(dbplyr)
library(knitr)
library(gridExtra)
library(grid)
library(ggplot2)
library(reshape2)
library(kableExtra)
```


```{r dataload, include=FALSE}
# Run the calculator - you should have edited this script in advance to contain the data you need.
#source(paste0(getwd(),"/Significance Calculator VB.R"))
```

```{r read_in_data, echo=FALSE}

stats_results_editorial_new_trending<- read.csv(paste0(getwd(),"/stats_results_editorial-new-trending.csv")) %>%filter(metric != 'clicks')
stats_results_binge_worthy<- read.csv(paste0(getwd(),"/stats_results_binge-worthy.csv"))%>%filter(metric != 'clicks')
stats_results_homepage<- read.csv(paste0(getwd(),"/stats_results_whole-homepage.csv"))%>%filter(metric != 'clicks')
stats_results_product<- read.csv(paste0(getwd(),"/stats_results_whole-product.csv"))%>%filter(metric != 'clicks')


var_totals_editorial_new_trending<-read.csv(paste0(getwd(),"/var_totals_editorial-new-trending.csv"))
var_totals_binge_worthy<-read.csv(paste0(getwd(),"/var_totals_binge-worthy.csv"))
var_totals_homepage<-read.csv(paste0(getwd(),"/var_totals_whole-homepage.csv"))
var_totals_product<-read.csv(paste0(getwd(),"/var_totals_whole-product.csv"))

hids_visits_summary<- read.csv(paste0(getwd(),"/hids_visits_summary.csv"))

#Add an "all ages" set to hids and visits data
hids_visits_summary<- 
  hids_visits_summary %>% 
  bind_rows(
    hids_visits_summary %>%
      group_by(exp_group) %>%
      summarise(hids = sum(hids),visits = sum(visits)) %>%
      mutate(age_range = 'all 16+')
    ) %>%
  mutate(hids2 = signif(hids, 3),
         visits2 = signif(visits, 3)) %>%
  select(-hids,-visits) %>%
  rename(hids = hids2, visits = visits2)
```


```{r define_functions, echo=FALSE}
get_uplift_table<-function(df, age_group, metric_name, comp_var){
  uplift_table<- df %>%
    filter(age_range == age_group &
             comparison %in% comp_var &
             metric == metric_name) %>% 
    mutate( uplift2 = ifelse(significance == 'Significant', uplift, 'NA'), #alter table for if value is not significant
            performance2 = ifelse(significance == 'Significant', performance, 'not significant')) %>%
    select(-uplift, -performance) %>%
    rename(uplift = uplift2, performance = performance2)%>%
    select(variable, comparison, metric, performance, uplift) %>%
    select(-metric)
  return(uplift_table)
}

#function to sumarise the total starts/clicks/compeltes and join to the number of hids and visits
get_summary_values<-function(metric_df, hids_visits_df ){
summary_values<-
  metric_df %>%
  mutate(
    clicks2 = signif(clicks, 3),
    starts2 = signif(starts, 3),
    completes2 = signif(completes, 3)
  ) %>%
  select(-clicks,-starts,-completes) %>%
  rename(clicks = clicks2,
         starts = starts2,
         completes = completes2) %>%
  left_join(hids_visits_df
,
    by = c("age_range" = "age_range",
           "variant" = 'exp_group')
  ) %>%
  select(age_range, variant, hids, visits,clicks, starts, completes)
return(summary_values)
}
```
## Experiment Summary & Headlines

### Overview
<br>

#### Hypothesis

<b>IF</b> we sort a list of programmes on the Featured and Binge Worthy series rows using the iRex sorting algorithm

<b>THEN</b> we will increase the consumption of content from these rows

<b>DUE TO</b> the iRex sorting algorithm serving more relevant content on these rows than the current sorting algorithm provided by Think Analytics

<br>

#### Duration & Audience
The experiment ran for **2 weeks** between **2021-02-11** and **2021-02-24** to **100%** of the audience on homepage. There were 4 variants (control, v1, v2, & v3) with approximately **2.3 million signed in users** in each experiment group. 

<br>

#### Test Duration & Sample Size
In the experiment design phase, we calculated the test should run for 2 weeks and reach 400,000 users or more to be able to see a 2% minimum detectable change.  
<br>
The experiment met both of these criteria.  
<br>

### Headline Results

<br>

##### Editorial New & Trending
```{r significance_summary_editorial_new_trending, echo=FALSE}
#See how many variant combinations are significant
signif_starts<-stats_results_editorial_new_trending %>%
  filter(metric =='starts') %>% 
  group_by(significance) %>%
  count() %>%
  ungroup() %>%
  mutate(percent= round(prop.table(n) * 100,0)) %>% 
  filter(significance == "Significant")
if(nrow(signif_starts) ==0) {
  signif_starts<- data.frame(significance = "Significant", n =0, percent = 0)
}

#See how many variant combinations are significant
signif_completes<-stats_results_editorial_new_trending %>%
  filter(metric =='completes') %>%
  group_by(significance) %>%
  count() %>%
  ungroup() %>%
  mutate(percent= round(prop.table(n) * 100,0)) %>%
  filter(significance == "Significant")
if(nrow(signif_completes) ==0) {
  signif_completes<- data.frame(significance = "Significant", n =0, percent = 0)
}
```

For this homepage module `r if(signif_starts$percent ==100 ) {"all of the"} else if(signif_starts$percent <100 & signif_starts$percent >=60) {"most of the"} else if(signif_starts$percent <160 & signif_starts$percent >=100) {"a few of the"} else {"less than 10% of" } `  metric comparisons showed significant results for the metric "starts" and `r if(signif_completes$percent ==100 ) {"all of the"} else if(signif_completes$percent <100 & signif_completes$percent >=60) {"most of the"} else if(signif_completes$percent <160 & signif_completes$percent >=100) {"a few of the"} else {"less than 10% of" } `  metric "completes" comparisons. There were between 1.2 and 1.4 millions clicks on the editorial new & trending rail for each variant, between 710,000 and 810,000 play starts (30s metric) and between 480,000 and 560,000 play completes (90% content competion). A detailed breakdown can be found on the module specific tab.

<br>
Across all users, **variant three performed the best** with an uplift for play compeltes of 8.8% whilst **variant two performed the worst** at 5.9% below the control.

```{r headline_table_editorial_new_trending, echo=FALSE}

age_range<-'all 16+'
rail_name<-'Editorial New Trending'
comparison_var<- c('control') #c('control', 'var1', 'var2', 'var3')

df<-left_join(
  get_uplift_table(stats_results_editorial_new_trending, age_range, 'starts', comparison_var),
  get_uplift_table(stats_results_editorial_new_trending, age_range, "completes",comparison_var),
  by = c("variable" = "variable", "comparison"="comparison")
)

df$uplift.x<- cell_spec(df$uplift.x, color = ifelse(df$uplift.x == 'NA', 'black',ifelse(df$uplift.x>0, 'green','red')))
df$uplift.y<- cell_spec(df$uplift.y, color = ifelse(df$uplift.y == 'NA', 'black', ifelse(df$uplift.y > 0, 'green','red')))
                                                    
df%>% 
kbl(booktabs = T, col.names = c("Variant", "Comparison", "Performance", "Uplift (%)","Performance", "Uplift (%)"), 
      caption = paste0(rail_name,": ",age_range),
    escape = F) %>%
  add_header_above(c(" " = 2,"Starts" =2, "Completes" = 2 ))%>%
  kable_styling(bootstrap_options =c("striped", "scale_down","hover")) %>%
  footnote(general = "Uplift is calculated for the variant relative to the control. A negative value means the variant performed worse than the comparison..")

```

<br>

##### Binge-Worthy
```{r significance_summary_binge_worthy, echo=FALSE}
#See how many variant combinations are significant
signif_starts<-stats_results_binge_worthy %>%
  filter(metric =='starts') %>% 
  group_by(significance) %>%
  count() %>%
  ungroup() %>%
  mutate(percent= round(prop.table(n) * 100,0)) %>% 
  filter(significance == "Significant")
if(nrow(signif_starts) ==0) {
  signif_starts<- data.frame(significance = "Significant", n =0, percent = 0)
}

#See how many variant combinations are significant
signif_completes<-stats_results_binge_worthy %>%
  filter(metric =='completes') %>%
  group_by(significance) %>%
  count() %>%
  ungroup() %>%
  mutate(percent= round(prop.table(n) * 100,0)) %>%
  filter(significance == "Significant")
if(nrow(signif_completes) ==0) {
  signif_completes<- data.frame(significance = "Significant", n =0, percent = 0)
}
```

For the this homepage module `r if(signif_starts$percent ==100 ) {"all of the"} else if(signif_starts$percent <100 & signif_starts$percent >=60) {"most of the"} else if(signif_starts$percent <160 & signif_starts$percent >=100) {"a few of the"} else {"less than 10% of" } `  metric comparisons showed significant results for the metric "starts" and `r if(signif_completes$percent ==100 ) {"all of the"} else if(signif_completes$percent <100 & signif_completes$percent >=60) {"most of the"} else if(signif_completes$percent <160 & signif_completes$percent >=100) {"a few of the"} else {"less than 10% of" } `  metric "completes" comparisons.  There were between 1.1 and 1.5 millions clicks on the binge-wothy rail for each variant, between 700,000 and 960,000 play starts (30s metric) and between 470,000 and 680,000 play completes (90% content competion). A detailed breakdown can be found on the module specific tab.

<br>

Across all users, **variant three performed the best** with an uplift for play compeltes of 13.1% whilst **variant two performed the worst** at 21.3% below the control.

```{r headline_table_binge_worthy, echo=FALSE}

age_range<-'all 16+'
rail_name<-'Binge Worthy'
comparison_var<- c('control') #c('control', 'var1', 'var2', 'var3')

df<-left_join(
  get_uplift_table(stats_results_binge_worthy, age_range, 'starts', comparison_var),
  get_uplift_table(stats_results_binge_worthy, age_range, "completes",comparison_var),
  by = c("variable" = "variable", "comparison"="comparison")
)

df$uplift.x<- cell_spec(df$uplift.x, color = ifelse(df$uplift.x == 'NA', 'black',ifelse(df$uplift.x>0, 'green','red')))
df$uplift.y<- cell_spec(df$uplift.y, color = ifelse(df$uplift.y == 'NA', 'black', ifelse(df$uplift.y > 0, 'green','red')))
                                                    
df%>% 
kbl(booktabs = T, col.names = c("Variant", "Comparison", "Performance", "Uplift (%)","Performance", "Uplift (%)"), 
      caption = paste0(rail_name,": ",age_range),
    escape = F) %>%
  add_header_above(c(" " = 2,"Starts" =2, "Completes" = 2 ))%>%
  kable_styling(bootstrap_options =c("striped", "scale_down","hover")) %>%
  footnote(general = "Uplift is calculated for the variant relative to the control. A negative value means the variant performed worse than the comparison..")

```
<br>

##### Whole Homepage
```{r significance_summary_whole_homepage, echo=FALSE}
#See how many variant combinations are significant
signif_starts<-stats_results_homepage %>%
  filter(metric =='starts') %>% 
  group_by(significance) %>%
  count() %>%
  ungroup() %>%
  mutate(percent= round(prop.table(n) * 100,0)) %>% 
  filter(significance == "Significant")
if(nrow(signif_starts) ==0) {
  signif_starts<- data.frame(significance = "Significant", n =0, percent = 0)
}

#See how many variant combinations are significant
signif_completes<-stats_results_homepage %>%
  filter(metric =='completes') %>%
  group_by(significance) %>%
  count() %>%
  ungroup() %>%
  mutate(percent= round(prop.table(n) * 100,0)) %>%
  filter(significance == "Significant")
if(nrow(signif_completes) ==0) {
  signif_completes<- data.frame(significance = "Significant", n =0, percent = 0)
}
```

For the whole homepage `r if(signif_starts$percent ==100 ) {"all of the"} else if(signif_starts$percent <100 & signif_starts$percent >=60) {"most of the"} else if(signif_starts$percent <160 & signif_starts$percent >=100) {"a few of the"} else {"less than 10% of" } `  metric comparisons showed significant results for the metric "starts" and `r if(signif_completes$percent ==100 ) {"all of the"} else if(signif_completes$percent <100 & signif_completes$percent >=60) {"most of the"} else if(signif_completes$percent <160 & signif_completes$percent >=100) {"a few of the"} else {"less than 10% of" } `  metric "completes" comparisons. There were aproximately 11 millions clicks on the homepage for each variant, between 8.5 million play starts (30s metric) and 6 million play completes (90% content competion). A detailed breakdown can be found on the homepage specific tab.

<br>
Across all users, **no variant had a significant impact on the homepage consumption**.

```{r headline_table_whole_homepage, echo=FALSE}

age_range<-'all 16+'
rail_name<-'Homepage'
comparison_var<- c('control') #c('control', 'var1', 'var2', 'var3')

df<-left_join(
  get_uplift_table(stats_results_homepage, age_range, 'starts', comparison_var),
  get_uplift_table(stats_results_homepage, age_range, "completes",comparison_var),
  by = c("variable" = "variable", "comparison"="comparison")
)

df$uplift.x<- cell_spec(df$uplift.x, color = ifelse(df$uplift.x == 'NA', 'black',ifelse(df$uplift.x>0, 'green','red')))
df$uplift.y<- cell_spec(df$uplift.y, color = ifelse(df$uplift.y == 'NA', 'black', ifelse(df$uplift.y > 0, 'green','red')))
 
##Commenting this out as the results are not significant                                                   
# df%>% 
# kbl(booktabs = T, col.names = c("Variant", "Comparison", "Performance", "Uplift (%)","Performance", "Uplift (%)"), 
#       caption = paste0(rail_name,": ",age_range),
#     escape = F) %>%
#   add_header_above(c(" " = 2,"Starts" =2, "Completes" = 2 ))%>%
#   kable_styling(bootstrap_options =c("striped", "scale_down","hover")) %>%
#   footnote(general = "Uplift is calculated for the variant relative to the control. A negative value means the variant performed worse than the comparison..")


```

<br>

##### Whole Product
```{r significance_summary_whole_product, echo=FALSE}
#See how many variant combinations are significant
signif_starts<-stats_results_product %>%
  filter(metric =='starts') %>% 
  group_by(significance) %>%
  count() %>%
  ungroup() %>%
  mutate(percent= round(prop.table(n) * 100,0)) %>% 
  filter(significance == "Significant")
if(nrow(signif_starts) ==0) {
  signif_starts<- data.frame(significance = "Significant", n =0, percent = 0)
}

#See how many variant combinations are significant
signif_completes<-stats_results_product %>%
  filter(metric =='completes') %>%
  group_by(significance) %>%
  count() %>%
  ungroup() %>%
  mutate(percent= round(prop.table(n) * 100,0)) %>%
  filter(significance == "Significant")

if(nrow(signif_completes) ==0) {
  signif_completes<- data.frame(significance = "Significant", n =0, percent = 0)
}
```

For the whole product `r if(signif_starts$percent ==100 ) {"all of the"} else if(signif_starts$percent <100 & signif_starts$percent >=60) {"most of the"} else if(signif_starts$percent <160 & signif_starts$percent >=100) {"a few of the"} else {"less than 10% of" } `  metric comparisons showed significant results for the metric "starts" and `r if(signif_completes$percent ==100 ) {"all of the"} else if(signif_completes$percent <100 & signif_completes$percent >=60) {"most of the"} else if(signif_completes$percent <160 & signif_completes$percent >=100) {"a few of the"} else {"less than 10% of" } `  metric "completes" comparisons. There were aproximately 44 millions clicks on the product for each variant, 33 million play starts (30s metric) and 23 million play completes (90% content competion). A detailed breakdown can be found on the product specific tab.

<br>
Across all users, **no variant had a significant impact on the product consumption**.

```{r headline_table_whole_product, echo=FALSE}

age_range<-'all 16+'
rail_name<-'product'
comparison_var<- c('control') #c('control', 'var1', 'var2', 'var3')

df<-left_join(
  get_uplift_table(stats_results_product, age_range, 'starts', comparison_var),
  get_uplift_table(stats_results_product, age_range, "completes",comparison_var),
  by = c("variable" = "variable", "comparison"="comparison")
)

df$uplift.x<- cell_spec(df$uplift.x, color = ifelse(df$uplift.x == 'NA', 'black',ifelse(df$uplift.x>0, 'green','red')))
df$uplift.y<- cell_spec(df$uplift.y, color = ifelse(df$uplift.y == 'NA', 'black', ifelse(df$uplift.y > 0, 'green','red')))
 
##Commenting this out as the results are not significant                                                   
# df%>%
# kbl(booktabs = T, col.names = c("Variant", "Comparison", "Performance", "Uplift (%)","Performance", "Uplift (%)"),
#       caption = paste0(rail_name,": ",age_range),
#     escape = F) %>%
#   add_header_above(c(" " = 2,"Starts" =2, "Completes" = 2 ))%>%
#   kable_styling(bootstrap_options =c("striped", "scale_down","hover")) %>%
#   footnote(general = "Uplift is calculated for the variant relative to the control. A negative value means the variant performed worse than the comparison..")


```

<br>

<br>
<br>
<br>
<b>Contact</b> <br>
email: `dataforce@bbc.co.uk`<br>
slack: #help-data-force


## Editorial New and Trending

<br>

### Statistical Overview

To assess the difference between our control and variant group we ran a parametric test (t-test) to establish the mean differences between each group for each metric and if the difference is statistically significant.  


A p-value < 0.05 indicates the difference is statistically significant, we can reject the null hypothesis and conclude the difference seen is not due to chance.  
<br>
<br>

### Statistical Results by Age Range
```{r stat results new trending, echo=FALSE, results = "asis"}
age_ranges<-data.frame(stats_results_editorial_new_trending$age_range) %>%unique()

for(age in 1: nrow(age_ranges)) {
age_range<-age_ranges[age,1]
rail_name<-'Editorial New Trending'
comparison_var<- c('control', 'var1', 'var2', 'var3')


df<-left_join(
  get_uplift_table(stats_results_editorial_new_trending, age_range, 'starts', comparison_var),
  get_uplift_table(stats_results_editorial_new_trending, age_range, "completes",comparison_var),
  by = c("variable" = "variable", "comparison"="comparison")
)

df$uplift.x<- cell_spec(df$uplift.x, color = ifelse(df$uplift.x == 'NA', 'black',ifelse(df$uplift.x>0, 'green','red')))
df$uplift.y<- cell_spec(df$uplift.y, color = ifelse(df$uplift.y == 'NA', 'black', ifelse(df$uplift.y > 0, 'green','red')))
                                                    
table<-df%>% 
kbl(booktabs = T, col.names = c("Variant", "Comparison", "Performance", "Uplift (%)","Performance", "Uplift (%)"), 
      caption = paste0(rail_name,": ",age_range),
    escape = F) %>%
  add_header_above(c(" " = 2,"Starts" =2, "Completes" = 2 ))%>%
  kable_styling(bootstrap_options =c("striped", "scale_down","hover")) %>%
  footnote(general = "Uplift is calculated for the variant relative to the control. A negative value means the variant performed worse than the comparison..")

print(table)
}

```

<br>

### Metric Summary

```{r var totals new trending, echo=FALSE, results = "asis"}

rail_name = "Editorial New and Trending"
age_range = 'all ages'

get_summary_values(var_totals_editorial_new_trending, hids_visits_summary)%>%
  kbl(booktabs = T, 
      col.names = c('Age Range', "Variant", "Users", "Visits", "Clicks", "Starts", "Completes"),
      caption = paste0(rail_name,": ",age_range),
    escape = F) %>%
  row_spec(c(1:4,9:12), background = "#f9f8f8")%>%
  #kable_styling(bootstrap_options = c("striped", "hover"))

kable_styling(bootstrap_options =c("hover","scale_down"))




```




<br>
<br>




<br>
<br>
<br>
<b>Contact</b> <br>
email: `dataforce@bbc.co.uk`<br>
slack: #help-data-force


